### 2023-03-23 main/chapter_2ljets.tex
add cutflow and rejection factors to cheat-sheet

>>>>

The power of each of these variables to select signals and exclude backgrounds
is hugely variable across our many signal models and regions of phase space.
For illustration, Table~\ref{tab:2ljets_ewk_acceff} reproduces some signal
efficiency numbers for the sum of yields in all $\twoljets$-electroweak signal
regions.
It finds a that only $0.0003\%$ of signal events are captured under the light
C1N2 model with
$m(\chargino_1, \neutralino_2) = 100\,\eV[G]$ and
$m(\neutralino_1) = 60\,\eV[G]$.
The reduced cross-sections for models with large masses are offset by their
more spectacular appearances, with a much larger capture rate of
for more extreme models.
For example, the corresponding capture rate it $0.64\%$ for the C1N2 model with
$m(\chargino_1, \neutralino_2) = 650\,\eV[G]$ and
$m(\neutralino_1) = 250\,\eV[G]$.
Detailed cut-flow tables,
Tables~\ref{aux:ewk:cutflowSRllbb} to~\ref{aux:ewk:cutflowSROffShell_2} of
Appendix~\ref{app:2ljets_cut_flows},
give more granular information into the effects of many intermediate
selection requirements across all signal regions for several representative
signal models.
Notably, $\mttwoll$ rejects substantial amounts of signal, although this
rejection is worthwhile for its larger rate of background rejection.

On background rejection performance,
Tables~\ref{tab:cutflows_CR-VZ} to~\ref{tab:cutflows_CR-DY} of
Appendix~\ref{app:2ljets_cut_flows} present cut-flow tables in the four control
regions of $\twoljets$-electroweak with background sample rates included.
These tables show that $\mttwoll$ selections are powerful for removing $\ttbar$
backgrounds, as expected, and that $\metsig$ selections beyond the
pre-selection requirement of $\metsig > 6$ drastically reduce most other
backgrounds.
Summed across all four control regions with data given in these tables,
the control region selections reduce background rates with a survival fraction
of $1.5\%$ relative to the pre-selection requirements of
Table~\ref{tab:2ljets_presel}.

\begin{table}[tp]
\centering
\begin{tabular}{ccl}
\multicolumn{3}{c}{C1N2}   \\
$m(\chargino_1, \neutralino_2)$ ($\eV[G]$)
& $m(\neutralino_1)$ ($\eV[G]$)
& $A\times\epsilon$ (\%)
\\[1.5ex]
\hline
% 0.0000028408852207408747
100 & 60 & 0.0003       \\
% 0.000007322904893685767
150 & 70 & 0.0007       \\
% 0.00041538437098791273
250 & 100 & 0.042       \\
% 0.002093724286276909
400 & 200 & 0.21     \\
% 0.0063561141231079175
650 & 250 & 0.64     \\
\end{tabular}
\\[2em]
\begin{tabular}{ccl}
\multicolumn{3}{c}{GMSB}  \\
$m(\neutralino_1)$  ($\eV[G]$)
& $B(\neutralino_1 \to h \gravitino)$
& $A\times\epsilon$ (\%)  \\[1.5ex]
\hline
% 0.00023984225213678648
200 & 50 & 0.02  \\
% 0.002095514599015893
500 & 80 & 0.21   \\
% 0.0161139463793303
700 & 0  & 1.6   \\
\end{tabular}
\caption[
]{%
Acceptance times efficiency (fraction of total production yields) in the union
of all $\twoljets$-electroweak signal regions, displayed for example C1N2 and
GMSB signal models.
Acceptance $A$ and efficiency $\epsilon$ are defined via truth-level
simulations as specified in the footnote from Table~\ref{tab:2ljets_discovery}.
This table is adapted from the $\twoljets$ paper~\cite{atlas2022searches}.%
}
\label{tab:2ljets_ewk_acceff}
\end{table}
